Goals and Tasks

### 2020-05-04 README.Rmd
clipped task list to readme

## Literature
* Section **4.3** in "Regression: Models, methods, and applications" by Ludwig Fahrmeir, Thomas Kneib, Stefan Lang, and Brian Marx, especially Section 2.9.1 on "Regression models for location, scale, and shape"

>>>>

## Literature
* Section **4.3** on "Boosting Linear Regression Models" in "Regression: Models, methods, and applications" by Ludwig Fahrmeir, Thomas Kneib, Stefan Lang, and Brian Marx
* Section **2.9.1** on "Regression models for location, scale, and shape" in ibd.
